Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
Adding @pacastillo 's review of Sophos and Blackberry+KNOX sections

%%%%FERGU-SOA
%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
Besides, there is an emerging research area in the field of BYOD. This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}. The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security. This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices. The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.

@@

The tool manages all employees' smartphones and tablets from a single-based console. This console monitors the devices since the initial set up and registration, until they log off. Other features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.

@@

Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation. They are not being successful in spite of their features. On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}. 
On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available on its last Galaxy smartphone generation. Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still semained delayed until it was apparently found insecure \cite{Samsung_insecure}. Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android} (see Section \ref{subsec:androidwork}).

@@

The main feature of KNOX is the use of different containers, or environments, for business and personal sides. Each one even includes its own graphical configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
A password is required in order to enter into the business side and, once \textit{logged in} in this container, no more passwords are needed for the business applications. The applications approved by the company IT department must meet Samsung security standards and, though it has been said that KNOX is a device-focused solution, it offered an API. This API would allow the company to access to over almost 205 predefined IT policies. With regard to information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files. In the same way, the user is not allowed to share data between the two environments.

>>>>

%%%%FERGU-SOA
%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
Besides, there is an emerging research area in the field of BYOD. This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}. 
Although some works present studies on its impact in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm. The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security. This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices. The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.

@@

The tool manages all employees' smartphones and tablets from a single-based console. This console monitors the devices since the initial set up and registration, until they log off. Remainder features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.

@@

Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they are not being successful in spite of their features. On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}. 
On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available for its last Galaxy smartphone generation. Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still remained delayed until it was apparently found insecure \cite{Samsung_insecure}. Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android} (see Section \ref{subsec:androidwork}).

@@

The main feature of KNOX is the use of different containers, or environments, for business and personal sides. Each one includes its own graphical configuration, suche as wallpapers, or colour themes, in order to be more easily recognised and distinguished by the user.
A password is required in order to enter into the business side and, once \textit{logged in} to this container, no more passwords are needed for the business applications. The applications approved by the company IT department must meet Samsung security standards and, though it has been said that KNOX is a device-focused solution, the company offered an API. This API would allow the company to access to over almost 205 predefined IT policies. With regard to information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files. In the same way, the user is not allowed to share data between the two environments.
